Software Ticket Quality

### 2017-11-27 proposal/mprop.tex
Continue work on lit review

@@

@@

\textbf{Summarizing Software Artifacts: A Case Study of Bug Reports}\cite{rastkar2010summarizing}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The main goal of the research was to determine if software artifacts could be summarized effectively and automatically so that developers would need only to analyze summaries instead of full software artifacts (i.e. in our case, bug reports). 
  \item \textbf{What was the method?}
  Firstly, they collected data to analyze from 4 different open source projects (Eclipse, Mozilla, Gnome, KDE). Then, they asked the volunteers (i.e. university students) to annotate the bug reports - write a summary of maximum 250 words in their own sentences. These human-produced annotations were then used by algorithms to learn how to effectively summarize a bug report.  Afterwards, the authors asked the end users of these bug reports, the software developers, to rate the summaries against the original bug reports. 
  \item \textbf{What did they learn?}
  They learned that existing conversation-based extractive summary generators trained on bug reports produce the best results. 
  \item \textbf{Relevance to our work}:
  As the paper revolves around conversations that are attached to a bug (i.e. comments) instead of the actual description of the bug, we can apply the technique described here maybe to generate summaries and analyze them as well in the overall context of ticket quality (maybe together with some sentiment analysis). 
\end{itemize}

\textbf{Software Quality \- The Elusive Target}\cite{kitchenham1996software}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to determine what makes for a good quality
    software project, as well as who are the people in charge of this aspect
    and how should they approach achieving it.
  \item \textbf{What was the method?}
    They tried to define quality in software projects and analyze techniques that 
    measure such quality by looking at other models proposed in different other  
    papers (e.g.\ McCall's quality model, ISO 9126).
  \item \textbf{What did they learn?}
    They learned that quality is very hard to define and there are various 
    factors which need to be taken into consideration, such as the business
    model of the company, the type of the software project (e.g.\ safety
    critical, financial) or the actors which are involved and how they
    coordinate the software activities.
  \item \textbf{Relevance to our work}: this paper is a key paper on software  
    quality and it can prove beneficial in our research by
    giving valuable insights into how software quality can be modeled, thus
    helping us in selecting good quality open source repositories to work with 
    (i.e.\ ticket selection and analysis).
\end{itemize}

\textbf{Code Quality Analysis in OSS}\cite{stamelos2002code}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The article tries to discuss and examine the quality of the source code
    delivered by open source projects.
  \item \textbf{What was the method?}
    They used a set of tools that could automatically inspect various aspects
    of source code. The authors analyzed the 6th release of the OpenSUSE project
    and examined only the components, which are defined by C functions in the
    programs.
  \item \textbf{What did they learn?}
    The research's results show that Linux applications have high quality 
    code standards that one might expect in an open source repository, but 
    the quality is lower than the one implied by the standard. More than half
    of the components were in a high state of quality, but on the other hand, 
    most lower quality components cannot be improved only by applying some
    corrective actions. Thus, even though not all the source code was in 
    an industrial standards shape, there is definitely room for further 
    improvement and open source repositories proved to be of good quality.
  \item \textbf{Relevance to our work}: this work completes the previous paper
    on software quality in general by looking specifically at quality in
    open source projects, which will be our main points for data collection.
\end{itemize}

>>>>

The work of \citet{kitchenham1996software} looks specifically at defining
quality in a software projects, as well as finding who are the people in charge of 
this and how should they approach achieving it. They tried to define quality 
in software projects and analyze techniques that measure such metrics by looking
at other models proposed in different other researches, such as McCall's quality
model or ISO 9126. However, they learned that quality is very hard to define and
there are various factors which need to be taken into consideration, such as the
business model of the company, the type of the software project (e.g. safety 
critical, financial sector) or the actors who are involved and how they coordinate
the software activities.

One other piece of data that is probably the most crucial in a software project
is code, and \citet{stamelos2002code} tried to discuss and examine the quality
of the source code delivered by open source projects. They used a set of tools
that could automatically inspect various aspects of source code, looking at
the 6th release of the OpenSUSE project and its components defined by C
functions. The research's results show that Linux applications have high quality 
code standards that one might expect in an open source repository, but 
the quality is lower than the one implied by the standard. More than half
of the components were in a high state of quality, but on the other hand, 
most lower quality components cannot be improved only by applying some
corrective actions. Thus, even though not all the source code was in 
an industrial standards shape, there is definitely room for further 
improvement and open source repositories proved to be of good quality.

@@

One other type of information that could be extracted and used for valuable
purposes is the summary of a bug report, as shown in the work of 
\citet{rastkar2010summarizing}. The authors wanted to determine if bug reports
could be summarized effectively and automatically so that developers would
need only to analyze summaries instead of full tickets. Firstly, they asked
university students to volunteer to annotate the bug reports collected from
various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
a summary of maximum 250 words in their own sentences. These human-produced 
annotations were then used by algorithms to learn how to effectively summarize a 
bug report.  Afterwards, the authors asked the end users of these bug reports, the 
software developers, to rate the summaries against the original bug reports.
They eventually learned that existing conversation-based extractive summary
generators trained on bug reports produce the best results.

@@
